### 2022-05-13 manuscript.Rmd
Revert colons in captions to bars

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : papaja::apa6_pdf
header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \renewcommand{\arraystretch}{0.59}
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=colon,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=colon,name=Fig.,textfont=normalfont}
---

>>>>

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : papaja::apa6_pdf
header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \renewcommand{\arraystretch}{0.59}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

### 2022-05-13 supplement.Rmd
Revert colons in captions to bars

## Supplementary Methods 1: Correlation between dependent samples

@@

## Supplementary Methods 2: Bias correction and sensitivity analysis for frequentist results

>>>>

## Supplementary Methods 1 | Correlation between dependent samples

@@

## Supplementary Methods 2 | Bias correction and sensitivity analysis for frequentist results
